\vspace{-1in} Demystifying the Computer Science \\PhD Admission in US Universities\\{\large A Guide for International Students

### 2023-10-06 demystify.tex
Updates from Overleaf

\section{Choosing Schools and Professors}
\subsection{Selecting and Ranking Schools for CS}
   \begin{center}
    \includegraphics[scale=0.5]{c1.png}
   \end{center}

@@

\subsection{Tenured or tenure-track faculty? Who do you choose?}

>>>>

\section{Choosing Schools and Professors}\label{sec:schoolsandprofs}

Choosing a school and an advisor is clearly one of the most important things in your mind when you apply to and especially when you get admitted to a PhD program in CS.  This is further complicated due to cultural differences and unfamiliarity of  international students to the US system and faculty.  I hope this section will clear some confusions and help you make more informed decision.

\subsection{Universities}

There are many types of universities in the US (as well as other countries). But here I mainly focus on the object of obtaining a Ph.D degree in CS.

\subsection{Schools that offer Ph.D. in CS}  Most university will have a "Computer Science" or CS-like programs. 
However, while many universities offer Ph.D. degree in their CS programs, many do not.  These universities might offer just Bachelor degrees (e.g., BS) and no graduate studies (i.e., no MS or Ph.D degrees), or they must just offer MS programs (but no PhD).

Thus, if your goal is Ph.D. in CS, you will have to filter out schools that do not offer such degree.  This might sound obvious but many students (even those in the US) get confused due to the large number of universities. For example, Penn State in University Park has Ph.D. in CS,  but Penn State in Harrisburg only has BS and MS in CS and Penn State in York only has BS in CS.  On the other hand, multiplication locations of the University of Texas, e.g., Austin, Dallas, Arlington, all have PhDs in CS. Also, some schools might offer PhDs in related fields, but not CS.

\subsubsection{R1, R2, ...}

\subsection{Selecting and Ranking Schools for CS}
   \begin{center}
    \includegraphics[scale=0.5]{c1.png}
   \end{center}

@@

\subsection{Choosing a Professor}

\subsubsection{Tenured, Tenure Track, Teaching,  Assistant Profs., Associate Profs}

\subsubsection{Tenured or tenure-track faculty? Who do you choose?}
